Compiling refinement types to dependent types

### 2020-07-24 tex/paper.tex
Add ADTs to the core language
Sigh.
Add a note on our extensions and the usage of equality

\newNTclass{gterm}
\newgterm x x
\newgterm v v
\newgterm n n

@@

We take $\lambda C$ \cite{TTFPLambdaC}
with a unit type as our core dependently typed language.
We conjecture that the introduction of units
does not break the usual metatheoretical properties of the system.

The syntax of the core language is presented in \figref{core_syntax},
the core $\lambda C$ typing rules are defined in \figref{core_typing}
and the rules for our extensions are defined in \figref{core_typing_exts}.

@@

\begin{figure}[ht]
  \footnotesize
  \drules[CT]{$\nonterm G \vdash \nonterm{ec}_1 : \nonterm{ec}_2$}{core typing}{Sort,Var,Weaken,Form,App,Abs,Conv}
  \caption{$\lambda C$ typing rules}
  \label{fig:core_typing}
\end{figure}
\begin{figure}[ht]
  \footnotesize
  \drules[CT]{$\nonterm G \vdash \nonterm{ec}_1 : \nonterm{ec}_2$}{core typing, extensions}{UnitType,UnitTerm}
  \caption{Our extensions typing rules}
  \label{fig:core_typing_exts}
\end{figure}

>>>>

\newNTclass{gterm}
\newgterm x x
\newgterm v v
\newgterm n n
\newgterm p \pi

@@

We take $\lambda C$ \cite{TTFPLambdaC}
extended with a unit type
and a restricted form of ADTs as our core dependently typed language.
We conjecture that these extensions
do not break the usual metatheoretical properties of the system,
and we explicitly prove progress and preservation theorems as a sanity check.

The syntax of the core language is presented in \figref{core_syntax},
the core $\lambda C$ typing rules are defined in \figref{core_typing}
and the rules for our extensions are defined in \figref{core_typing_exts}.
Note that the \textsc{CT-ADTCase} rule uses the equality $\equiv$,
which is a derived form defined later.

@@

\begin{figure}[ht]
  \footnotesize
  \drules[CT]{$\nonterm G \vdash \nonterm{ec}_1 : \nonterm{ec}_2$}{core typing}{Sort,Var,Weaken,Form,App,Abs,Conv}
  \caption{$\lambda C$ typing rules}
  \label{fig:core_typing}
\end{figure}
\begin{figure}[ht]
  \footnotesize
  \drules[CT]{$\nonterm G \vdash \nonterm{ec}_1 : \nonterm{ec}_2$}{core typing, extensions}{UnitType,UnitTerm,ADTForm,ADTCon,ADTCase}
  \caption{Typing rules for our extensions to $\lambda C$}
  \label{fig:core_typing_exts}
\end{figure}
